Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-06-01 paper/IJCAI19/paper.tex
acks
cr ready

The contributions of this work are:
\begin{itemize}
 \item[1)]~an empirical study, using
real-world applications and bugs, on the combination of \ds{} and
\sfl{} for bug localization of \emph{Java} faulty programs and
\item[2)]~a
tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination.
\end{itemize}
The
tool as well as a replication package will be available once
double-blind requirements are lifted.

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has $1,000$ lines, Lithium sets the
initial chunk size to $512$ lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} 
(Accessed \today)}. Our implementation is publicly available at 
\url{https://github.com/damorim/lithium-slicer}.

@@

We used subject programs from the \dfj{}
benchmark~\cite{just-defects4j-issta2014} in our evaluation.
Table~\ref{tab:df4j} shows size, number of tests, and number of
faults, for each considered program. Two faults from \cmath{} were not
considered because we were unable to reproduce them in our
environment.

\lang{} is a library providing utility functions for the
     {\small\texttt{java.lang}} API. \cmath{} is a library of
     self-contained mathematics and statistics components.\comments{
       The \closure{} is a toolset for turning JavaScript files into
       smaller scripts for faster download and execution in the
       browser.} \chart{} is a Java library for creating charts.
     \jtime{} is a library for manipulating date and time\comments{,
       providing a simpler API compared to
       {\small\texttt{java.util.Date}}}. \mockito{} is a mocking
     testing framework.

@@

        \lang{}            & 100.0 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\\midrule
        Total          & 87.3 & 91.2\\

@@

\begin{table}[h]
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
\begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty
    statements appears at the report of the technique. Higher is better.}
  \label{table:fsws}
\end{table}

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
		\vspace{-0.4cm}
		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
		\label{fig:diagnosis}
\end{figure}

@@

\begin{figure}[h]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.45\textwidth]{figures/boxplot.pdf}
		\vspace{-0.4cm}

@@

In the following, we present statistical analysis of the techniques.
Table~\ref{table:st} reports descriptive statistics about the
distributions of $C$ for the techniques under different values of $k$.
In bold, we present the results for the $227$ faults corresponding to
the cases where $\Delta(C)\geq{}0$. The number in parentheses are
relative to the dataset including all faults.

%% These results show that \ds{}
%% improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
%% the average ranking of all faulty statements, when considering
%% $k=10$.

We observe the following when considering the faults which can benefit
from \comb\ (numbers in bold). For $k=5$, \comb\ achieves a mean
improvement of $41.1$ ($9.57\%$ on average) statements on the ranking
and an impressive maximum ranking improvement of $3171$ ($96.7\%$ on
average) statements. For $k=10$, \combpar{k} achieves a mean
improvement of $19$ ($13.35\%$ on average) statements on the ranking
and a maximum ranking improvement of $209$ ($73.7\%$ on average)
statements. Such difference is justified by the fact that entire files
are discarded in \combpar{5}, whose statements are included in the
ranking of \combpar{10}. Consequently, the improvements obtained by
the technique will not be as high if slicing on these additional files
is unable to aggressively and safely discard statements. This also
shows that slicing files, in addition to slicing statements from those
files, is very beneficial for fault localization performance.

@@

\begin{figure}[h]
	\vspace{-1cm}
		\includegraphics[width=0.48\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.3cm}
\end{figure}

>>>>

The contributions of this work are:
\begin{itemize}
 \item[1)]An empirical study, using
real-world applications and bugs, on the combination of \ds{}-\sfl{} for bug localization of \emph{Java} faulty programs.
\item[2)]A
tool\footnote{Tool and dataset available at/through \url{https://github.com/damorim/lithium-slicer} (Accessed \today)}, dubbed \comb{}, implementing the \ds{}-\sfl{} combination. 
\end{itemize}

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has $1,000$ lines, Lithium sets the
initial chunk size to $512$ lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} 
(Accessed \today)}.

@@

We used subject programs from the \dfj{}
benchmark~\cite{just-defects4j-issta2014} in our evaluation.
Table~\ref{tab:df4j} shows size, number of tests, and number of
faults, for each considered program. Two faults from \cmath{} were not
considered because we were unable to reproduce them in our
environment. \lang{} is a library providing utility functions for the
     {\small\texttt{java.lang}} API. \cmath{} is a library of
     self-contained mathematics and statistics components.\comments{
       The \closure{} is a toolset for turning JavaScript files into
       smaller scripts for faster download and execution in the
       browser.} \chart{} is a Java library for creating charts.
     \jtime{} is a library for manipulating date and time\comments{,
       providing a simpler API compared to
       {\small\texttt{java.util.Date}}}. \mockito{} is a mocking
     testing framework.

@@

        \lang{}            & 96.9 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\\midrule
        Total          & 87.3 & 91.2\\

@@

\begin{table}[h]
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
\begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 96.9 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 86.5 & 83.5 & 90.4\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty
    statements appears at the report of the technique. Higher is better.}
  \label{table:fsws}
\end{table}

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\textwidth]{figures/performance.png}
		\vspace{-0.4cm}
		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
		\label{fig:diagnosis}
\end{figure}

@@

\begin{figure}[h]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.45\textwidth]{figures/boxplot.png}
		\vspace{-0.4cm}

@@

In the following, we present statistical analysis of the techniques.
Table~\ref{table:st} reports descriptive statistics about the
distributions of $C$ for the techniques under different values of $k$.
In bold, we present the results for the $227$ faults corresponding to
the cases where $\Delta(C)\geq{}0$. The number in parentheses are
relative to the dataset including all faults.
We observe the following when considering the faults which can benefit
from \comb\ (numbers in bold). For $k=5$, \comb\ achieves a mean
improvement of $41.1$ ($9.57\%$ on average) statements on the ranking
and an impressive maximum ranking improvement of $3171$ ($96.7\%$ on
average) statements. For $k=10$, \combpar{k} achieves a mean
improvement of $19$ ($13.35\%$ on average) statements on the ranking
and a maximum ranking improvement of $209$ ($73.7\%$ on average)
statements. Such difference is justified by the fact that entire files
are discarded in \combpar{5}, whose statements are included in the
ranking of \combpar{10}. Consequently, the improvements obtained by
the technique will not be as high if slicing on these additional files
is unable to aggressively and safely discard statements. This also
shows that slicing files, in addition to slicing statements from those
files, is very beneficial for fault localization performance.

@@

\begin{figure}[h]
	\vspace{-2cm}
		\includegraphics[width=0.48\textwidth]{figures/heatmap_seg_result.png}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.3cm}
\end{figure}
